---
output: 
  github_document: default
  html_document:
    self_contained: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE)
```

## Scripts

This repository contains the scripts implementing for the network inference 
method of the article (Marti-Marimon *et al*, 2018). It can be installed with:
```{r install, eval=FALSE}
devtools::install_github("tuxette/internet3D")
```
The main functions of the package are `build.network` and `bootstrap.build`.


## Supplementary files

After installation, supplementary files with the different networks described 
in the article are in:
```{r networksLoc, eval=FALSE}
system.file("results/network0.graphml", package = "internet3D")
```
(and similarly for `network1`, `network2` and `network3`). They can be loaded 
within **R** with 
```{r networksImport, message=FALSE}
library(igraph)
net0 <- system.file("results/network0.graphml", package = "internet3D")
net0 <- read_graph(net0, format = "graphml")
net0
```

The files are also directly accessible in this repository in `inst/results` and
can be read with any standard tool for graph visualization (*e.g.*, Gephi,
https://gephi.org/)